---
title: "Class 15: Genomics I"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Read sample genotypes data from ENSEMBLE 

We downloaded genotype data from ENSEMBLE on the MXL Mexican Ancestry in Los Angeles, California dataset.

What proportion of this data are G/G etc? 

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8069176.csv")

head(mxl)
```

We want to look at the second column that contains the genotype info

```{r}
table(mxl$Genotype..forward.strand.)
```

## RNA-Seq result analysis for different genotypes of this SNP

```{r}
expr <- read.table("rs8067378_ENSG00000172057.6.txt")
head(expr)
```

```{r}
summary( expr[expr$geno == "G/G", ]$exp, breaks=20)
```

```{r}
summary( expr[expr$geno == "A/G", ]$exp, breaks=20)
```

```{r}
summary( expr[expr$geno == "A/A", ]$exp, breaks=20)
```

## Try a boxplot
 
We will use the `boxplot()` function and the input data will be **expr**.
How do we draw a useful plot? 

```{r}
boxplot(exp ~ geno , data=expr, notch = TRUE)
```

How many samples are we looking at here?
```{r}
nrow(expr)
```



```{r}
hist( expr[expr$geno == "G/G", ]$exp, breaks=20)
```





