---
title: "Structural Bioinformatics (pt.1)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PDB Statistics
Download a CSV file from the PDB site (accessible from “Analyze” > “PDB Statistics” > “by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project and use it to answer the following questions:

> Q: What percentage of structures in the PDB are solved by X-Ray and Electron Microscopy.

```{r}
stats <- read.csv("Data Export Summary.csv", row.names = 1)
stats
```


```{r}
ans <- round(stats$Total / sum(stats$Total) * 100, 2)
names(ans) <- rownames(stats)
ans
```


> Q: What proportion of structures in the PDB are protein?

```{r}
round( sum(stats$Proteins) / sum(stats$Total) * 100, 2)

```


> Q: Type HIV in the PDB website search box on the home page and determine how many HIV-1 protease structures are in the current PDB?

## 2. Using bio3d to analyse protein structure data 

Use the bio3d package from CRAN. 

```{r}
library(bio3d)

pdb <- read.pdb("1hsg")
pdb
```


# Install packages in the R console not your Rmd

Adenylate kinase structures from the PDB for analysis





```{r}
hits <- NULL
hits$pdb.id <- c('1AKE_A','4X8M_A','6S36_A','6RZE_A','4X8H_A','3HPR_A','1E4V_A','5EJE_A','1E4Y_A','3X2S_A','6HAP_A','6HAM_A','4K46_A','4NP6_A','3GMT_A','4PZL_A')
```

Download and parse these structures 
# Download releated PDB files
```{r}
library(bio3d)
files <- get.pdb(hits$pdb.id, path="pdbs", split=TRUE, gzip=TRUE)
```

Align and superpose structures 
```{r}
# Align releated PDBs
pdbs <- pdbaln(files, fit = TRUE, exefile="msa")
```

```{r}
library(bio3d.view)
view(pdbs)
```

```{r}
pc <- pca(pdbs)
plot(pc)
```

```{r}
library(rgl)
view(pdbs)
rglwidget(elementId = "plot3drgl")
```










