---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```
 
```{r}
library(dplyr)

virus %>% group_by(Country.Region) %>%
  summarize(sum(cases)) %>%
  arrange()
```

> Q1. How many total infected cases are there around the world?

```{r}
total_cases <- sum(virus$cases)
total_cases
```
> Q2. How many deaths linked to infected cases have there been?
Lets have a look at the *$type* column 

```{r}
table(virus$type)
```

```{r}
inds <- virus$type == "death"
death_cases<- sum(virus[inds,"cases"])
```

> Q3. What is the overall death rate?

Percent death 
```{r}
round(death_cases/total_cases * 100, 2)
```

> Q4. What is the death rate in "Mainland China"?

```{r}
china.cases <- virus$Country.Region == "Mainland China"

china.death_cases <- sum(virus[china.cases,"cases"])
```

```{r}
round(china.death_cases/total_cases * 100, 2)
```

> Q5. What is the death rate in Italy, Iran and the US?

```{r}
Italy.cases <- virus$Country.Region == "Italy"
Italy.death_cases <- sum(virus[Italy.cases, "Italy"])
```

```{r}
round(Italy.death_cases/total_cases * 100, 2)
```


```{r}
Iran.cases <- virus$Country.Region == "Iran"
Iran.death_cases <- sum(virus[Iran.cases, "Iran"])
```

```{r}
round(Iran.death_cases/total_cases * 100, 2)
```

```{r}
US.cases <- virus$Country.Region == "US"
US.death_cases <- sum(virus[US.cases, "US"])
```

```{r}
round(US.death_cases/total_cases * 100, 2)
```

